---
title: "Lab 01 - Hello R"
author: "Cailey Fay"
date: "10.4.25"
output: 
  html_document: 
    highlight: tango
    df_print: default
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
# library(datasauRus)
library(ggpedigree)
```

## Exercises

### Exercise 1

1846 rows and 3 columns.

### Exercise 2

The answers for this exercise are already provided to help guide you. Clean up the narrative to reflect what you want to submit. Let’s break it into steps:

First, let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next, let's calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The correlation between x and y is -.064. 


### Exercise 3

Next, lets plot the star:

```{r plot-star}
 star <- datasaurus_dozen %>%
     filter(dataset == "star")

ggplot(data = star, mapping = aes(x=x, y=y)) + geom_point()
```

Next, let's calculate the correlation between x and y:  

```{r cor-star}
 star %>%
 summarize(r=cor(x,y))
```
The correlation is -.063. Star and Dino have the just about the same r value. 


### Exercise 4

To plot the circle and find the correlation between x and y: 

```{r}
 circle <- datasaurus_dozen %>%
 filter(dataset == "circle")
 ggplot(data = circle, mapping = aes(x=x, y=y))+ geom_point()
```

```{r}
circle %>%
 summarize(r=cor(x,y))
```
The correlation between x and y is -.068, which is also very similar to the star and dino correlations. 

### Exercise 5

Finally, to make fun colorful plots and find their respective correlations between x and y: 

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
    geom_point() +
    facet_wrap(~dataset, ncol = 3) +
    theme(legend.position = "none")

#correlations
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```


